Discrete Quantum Theories and Computing

### 2018-12-02 dissertation.tex
dissertation.lyx Abstract updating...

We begin by replacing the continuum of complex numbers by discrete
finite fields in quantum theory. The simplest theory, defined over
unrestricted finite fields, is so weak that it only predict whether
the measure result is possible or impossible. Its computational model
is also weak that it cannot express Deutsch's algorithm, but, paradoxically,
is also so powerful that it can be used to solve the $\usat$ problem,
which is as hard as a general $\NP$-complete problem.

Our second framework employs only finite fields over prime numbers
of the form $4\ell+3$, which possess no solutions to $x^{2}+1=0$,
and thus permit an elegant complex representation of the finite field
by adjoining $\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit
system are in principle enumerable, we can count the number of states,
and determine the proportions of entangled and unentangled states.
We tried define its measurement process in three different approaches.
For the model only predicting possible or impossible, we have solutions
to deterministic quantum algorithms such as Deutsch's algorithm, but
unnaturally strong computational power may still occur. In an improved
model, the cardinal probability of measurement results could be predicted
locally. In the local ordered region, the unnaturally computational
power is ruled out and the probabilistic Grover search algorithm can
be implemented. However, lacking arithmetic operations on cardinal
probabilities, expectation values cannot be defined easily. Since
arithmetic operations works with conventional probability measures,
we consider quantum probability measures over finite fields, but we
haven't found a consistent way to treat them in general.

>>>>

We begin by replacing the continuum of complex numbers by discrete
finite fields in quantum theory. The simplest theory, defined over
unrestricted finite fields, is so weak that it cannot express Deutsch's
algorithm, but, paradoxically, is also so powerful that it can be
used to solve the $\usat$ problem, which is as hard as a general
$\NP$-complete problem.

Our second framework employs only finite fields over prime numbers
of the form $4\ell+3$, which possess no solutions to $x^{2}+1=0$,
and thus permit an elegant complex representation of the finite field
by adjoining $\rmi=\sqrt{-1}$. Because the states of a discrete $n$-qubit
system are in principle enumerable, we can count the number of states,
and determine the proportions of entangled and unentangled states.
Depending on how we model the measurement process, this improved framework
can be used to implement deterministic Deutsch's algorithm and the
probabilistic Grover search algorithm in a local region, but we still
haven't found a consistent way to treat quantum probability measures
in general.
